An Engineered Empirical Burnstein Bound

### 2018-08-21 paper/main.tex
update paper

\begin{aug}
\author{\fnms{Mark} \snm{Burgess}\corref{}\thanksref{t1}
\ead[label=e1]{mark.burgess@anu.edu.au}
\ead[label=e2]{markburgess1989@gmail.com}}
\thankstext{t1}{A great thanks to Archie Chapman, Paul Scott and Sylvie Thiebaux; for Academic advice and encouragement!}
\address{Mark Alexander Burgess\\College of Engineering \& Computer Science\\Australian National University\\Canberra, ACT, Australia, 2600\\\printead{e1}\\
\printead{e2}}
\affiliation{Australian National University}
\end{aug}

@@

\begin{abstract}
We derive a stronger Empirical Burnstein Bound (EBB) using a combination of probability unions and Chernoff bounds for the mean of samples and mean of sample squares.
Like other EBBs, our EBB is a concentration inequality for the divergence of the sample mean from the population mean in terms of the sample variance.
The new EBB is numerically solved and compared against previous work, And for context it is also compared against a bound with perfect information about the variance.
The analysis reveals that our technique can shrink existing probability bounds by about a third, and that perfect variance information would reduce it by about a third again.
\end{abstract}

@@

\begin{keyword}
\kwd{Concentration inequality}
\kwd{Chernoff bounds}
\kwd{Hoeffdings inequality}
\kwd{Emperical Burnstein Bound}
\end{keyword}

>>>>

\begin{aug}
\author{\fnms{Mark} \snm{Burgess}\corref{}\thanksref{t1}
\ead[label=e1]{mark.burgess@anu.edu.au}
\ead[label=e2]{markburgess1989@gmail.com}}
\thankstext{t1}{A great thanks to Archie Chapman, Paul Scott and Sylvie Thi{\'e}baux; for Academic advice and encouragement!}
\address{Mark Alexander Burgess\\College of Engineering \& Computer Science\\Australian National University\\Canberra, ACT, Australia, 2600\\\printead{e1}\\
\printead{e2}}
\affiliation{Australian National University}
\end{aug}

@@

\begin{abstract}
We derive a stronger Empirical Burnstein Bound (EBB) using a combination of probability unions and Chernoff bounds for the mean of samples and mean of sample squares.
Like other EBBs, our EBB is a concentration inequality for the divergence of the sample mean from the population mean in terms of the sample variance.
The new EBB is numerically solved and compared against previous work, and for context it is also compared against a bound with perfect information about the variance.
The analysis reveals that our technique can shrink existing probability bounds by about a third, and that perfect variance information would reduce it by about a third again.
\end{abstract}

@@

\begin{keyword}
\kwd{Concentration inequality}
\kwd{Chernoff bounds}
\kwd{Hoeffding's inequality}
\kwd{Empirical Burnstein Bound}
\end{keyword}
